---
title: 'Lab 2: Regression to Study the Spread of Covid-19'
author: 'w203: Statistics for Data Science'
date: "10/28/2020"
output:
  pdf_document: default
  html_document: default
---
```{r setup, include=FALSE, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(readxl)
library(dplyr)
library(stringr)
library(tidyverse)
library(tidyr)
library(ggplot2)
library(Hmisc)
library(corrr)
library(ggplot2)
library(patchwork)
library(stargazer)
library(sandwich)
library(car)

```

### Data Cleaning

## State Characteristics
```{r state characteristics read data, include=FALSE}
#read state characteristics data
data_state_characteristics <- read.csv(file = 'COVID-19 US state policy database (CUSP) - State Characteristics.csv')
```

```{r clean data, include=FALSE}
#lower case all headers and remove last row which is empty
data_state_characteristics <- head(data_state_characteristics,-1)
names(data_state_characteristics) <- tolower(names(data_state_characteristics))

```

```{r export, include=FALSE}
#save CSV
write.csv(data_state_characteristics,"state_characteristics_clean.csv", 
          row.names = FALSE)
```


## State of Emergency
```{r State of emergency data, include="FALSE"}

file_path = "COVID-19 US state policy database (CUSP).xlsx"

df_emr <- read_xlsx(path = file_path,
                sheet = "State of Emergency",
                range = "B1:E52",
                col_types = c("text", "numeric", "date", "date"),
                trim_ws = TRUE,
                na = "0")

names(df_emr) <- str_replace_all(names(df_emr), c(" " = ".", "&" = "."))

df_emr$emr.last.update <- seq(ISOdate(2021,3,17), ISOdate(2021,3,17), length.out = 51)

df_emr <- mutate(df_emr, emr.closed.days = ifelse(is.na(State.of.emergency.issued), 0,
                                              ifelse(is.na(State.of.emergency.expired), emr.last.update - State.of.emergency.issued,
                                                    State.of.emergency.expired - State.of.emergency.issued)))

# create indicator if state had state of emergency
df_emr <- mutate(df_emr, emr.flag = ifelse(emr.closed.days > 0, 1, 0) )

# drop unnecessary columns
df_emr <- subset(df_emr, select = -c(State.FIPS.Code, State.of.emergency.issued,
                                     State.of.emergency.expired,
                                     emr.last.update))

```

## Stay at home
```{r Stay at Home, include="FALSE"}
df_stayhm <- read_xlsx(path = file_path,
                sheet = "Stay at Home",
                range = "B1:G52",
                col_types = c("text", "numeric", "date", "numeric", "date", "date"),
                trim_ws = TRUE,
                na = "0")

names(df_stayhm) <- str_replace_all(names(df_stayhm), c(" " = ".", "/" = ".", "\\*" = "", "-" = "."))

# last date data was updated according to excel ("Information" sheet)
df_stayhm$stayhm.last.update <- seq(ISOdate(2021,3,17), ISOdate(2021,3,17), length.out = 51)

# these states did not have stay at home orders, they provided optional guidance
# Their order start dates are also empty in original data
df_stayhm[df_stayhm$State.Abbreviation == "CT", "End.stay.at.home.shelter.in.place"] <- NA
df_stayhm[df_stayhm$State.Abbreviation == "KY", "End.stay.at.home.shelter.in.place"] <- NA
df_stayhm[df_stayhm$State.Abbreviation == "OK", "End.stay.at.home.shelter.in.place"] <- NA
df_stayhm[df_stayhm$State.Abbreviation == "TX", "End.stay.at.home.shelter.in.place"] <- NA


# data is clean, calculate duration of order to stay home
df_stayhm <- mutate(df_stayhm, stayhm.duration.days = ifelse(is.na(Stay.at.home.shelter.in.place), 0,
                                              ifelse(is.na(End.stay.at.home.shelter.in.place), 0,
                                                    End.stay.at.home.shelter.in.place - Stay.at.home.shelter.in.place)))

# create indicator if state had stay at home order
df_stayhm <- mutate(df_stayhm, stayhm.flag = ifelse(stayhm.duration.days > 0, 1, 0) )

# drop unnecessary columns
df_stayhm <- subset(df_stayhm, select = -c(State.FIPS.Code,
                                            stayhm.last.update,
                                            Stay.at.home.shelter.in.place,
                                            End.stay.at.home.shelter.in.place,
Stay.at.home.order.issued.but.did.not.specifically.restrict.movement.of.the.general.public))
```

## Religious gatherings
```{r Religious gatherings data, include="FALSE"}

# set indicator if religious gatherings were exempt
df_stayhm <- mutate(df_stayhm, relgn.gathering.banned.flag = ifelse(is.na(Religious.Gatherings.Exempt.Without.Clear.Social.Distance.Mandate), 1, 0) )

# drop unnecessary columns
df_stayhm <- subset(df_stayhm, select = -c(Religious.Gatherings.Exempt.Without.Clear.Social.Distance.Mandate))

```

## Face Masks
```{r Face masks data, include="FALSE"}

df_facemsk <- read_xlsx(path = file_path,
                sheet = "Face Masks",
                range = "B1:K52",
                col_types = c("text", "numeric", "date", "date", "numeric", 
                              "numeric", "numeric", "date", "date", "date"),
                trim_ws = TRUE,
                na = "0")

names(df_facemsk) <- str_replace_all(names(df_facemsk), c(" " = ".", "/" = "."))

# excel says last reviewed date was 2020/09/25 but doc contains data until 2021/03/16
df_facemsk$facemsk.last.update <- seq(ISOdate(2021,3,16), ISOdate(2021,3,16), length.out = 51)

# Montana (MT) did not have a state wide mask mandate (only implemented in a few counties)
df_facemsk[df_facemsk$State.Abbreviation == "MT", "End.face.mask.mandate"] <- NA

# data is clean, calculate duration of order to stay home
df_facemsk <- mutate(df_facemsk, facemsk.duration.days = 
                                  ifelse(is.na(Public.face.mask.mandate), 0,
                                    ifelse(is.na(End.face.mask.mandate),
                                           facemsk.last.update - Public.face.mask.mandate,
                                      End.face.mask.mandate - Public.face.mask.mandate)))


# set indicator if face mask orders were in place
df_facemsk <- mutate(df_facemsk, facemsk.mandate.flag = ifelse(facemsk.duration.days > 0, 1, 0) )

# set indicator if there was legal enforcement of face masks
# all NA values in excel are 0, so set them to 0 in data frame
df_facemsk <- mutate(df_facemsk, No.legal.enforcement.of.face.mask.mandate = 
                                  ifelse(is.na(No.legal.enforcement.of.face.mask.mandate), 0, 1) )

# create flag for all states that enforced face masks
df_facemsk <- mutate(df_facemsk, facemsk.enforced.flag = 
                                  ifelse(No.legal.enforcement.of.face.mask.mandate == 1, 0, 1) )

# drop unnecessary columns
df_facemsk <- subset(df_facemsk, select = -c(State.FIPS.Code,
                                             Public.face.mask.mandate,
                                             End.face.mask.mandate,
                                             Business.face.mask.mandate,
                                             facemsk.last.update,
Second.mandate.for.facemasks.by.all.individuals.in.public.places,
Face.mask.mandate.enforced.by.fines,
Face.mask.mandate.enforced.by.criminal.charge.citation,
No.legal.enforcement.of.face.mask.mandate,
Attempt.by.state.government.to.prevent.local.governments.from.implementing.face.mask.orders
))

# rename columns
#colnames(df)[2] <- "newname_for_col_2"

```

## Closures and re-openings
```{r Closures and re-openings data, include="FALSE"}
df <- read_xlsx(path = file_path,
                sheet = "Closures & Reopening",
                range = "A1:AO52",
                col_types = c("text", "text", "numeric",
                              "date", "date", "date", "date", "date",
                              "date", "date", "date", "date", "numeric",
                              "date", "date", "date", "numeric", "date",
                              "date", "date", "date", "date", "date",
                              "date", "date", "date", "date", "date",
                              "date", "date", "date", "date", "date",
                              "date", "date", "date", "date", "date",
                              "date", "date", "date"),
                trim_ws = TRUE,
                na = "0"
                )

names(df) <- str_replace_all(names(df), c(" " = ".", "&" = ".", "-" = ".", "/" = "."))

# Drop columns not used in EDA and calculations (bars, casinos, hair salons, etc)
df <- subset(df, select = -c(State, State.FIPS.Code,
                             Closed.K.12.public.schools,
                             Closed.bars,
                             Closed.casinos,
                             Reopened.bars,
                             Reopened.casinos,
                             Closed.bars.x2,
                             Reopened.bars.x2,
                             Closed.bars.x3,
                             Closed.casinos.x2,
                             Reopened.casinos.x2,
                             Closed.other.non.essential.businesses,
                             Mention.of.tribal.casinos,
                             Closed.businesses.overnight,
                             Began.to.reopen.businesses.statewide,
                             Reopened.hair.salons.barber.shops,
                             Reopened.religious.gatherings, # this is available elsewhere
                             Reopened.other.non.essential.retail,
                             Allowed.businesses.to.reopen.overnight,
                             Began.to.re.close.bars,
                             Closed.hair.salons.barber.shops.x2
                             ))

###########################################################################
# Nursing homes - visits banned
df$nursinghm.last.update <- seq(ISOdate(2020,10,2), ISOdate(2020,10,2), length.out = 51)

# number of days visits banned to nursing homes  
df <- mutate(df, nursinghm.closed.days = ifelse(is.na(Banned.visitors.to.nursing.homes), 0,
                                        nursinghm.last.update - Banned.visitors.to.nursing.homes
                                        ))

# Create indicator column for restaurants
df <- mutate(df, nursinghm.flag = ifelse(nursinghm.closed.days > 0, 1, 0) )

# Drop restaurant columns not needed
df <- subset(df, select = -c(Banned.visitors.to.nursing.homes, nursinghm.last.update))


###########################################################################
# Restaurants - days closed x1
df <- mutate(df, rest.closed.days.x1 = ifelse(is.na(Reopened.restaurants), 0,
                                              ifelse(is.na(Closed.restaurants), 0,
                                                    Reopened.restaurants - Closed.restaurants)))
# Restaurants - days closed x2
# Big assumption: using date of March 4th 2021 as final date of re-opening ("Information" sheet, row 80)
df$rest.last.update <- seq(ISOdate(2021,3,4), ISOdate(2021,3,4), length.out = 51)

df <- mutate(df, rest.closed.days.x2 = ifelse(is.na(Closed.restaurants.x2), 0,
                                              ifelse(is.na(Reopened.restaurants.x2), rest.last.update - Closed.restaurants.x2,
                                                    Reopened.restaurants.x2 - Closed.restaurants.x2)))

# Restaurants - days closed x3
df <- mutate(df, rest.closed.days.x3 = ifelse(is.na(Closed.restaurants.x3), 0,
                                              ifelse(is.na(Reopened.restaurants.x3), rest.last.update - Closed.restaurants.x3,
                                                    Reopened.restaurants.x3 - Closed.restaurants.x3)))

# Restaurants - total duration
df <- mutate(df, rest.duration.days = rest.closed.days.x1 + rest.closed.days.x2 + rest.closed.days.x3)

# Create indicator column for restaurants
df <- mutate(df, rest.flag = ifelse(rest.duration.days > 0, 1, 0) )

# Drop restaurant columns not needed
df <- subset(df, select = -c(Closed.restaurants, Reopened.restaurants,
                             Closed.restaurants.x2, Reopened.restaurants.x2,
                             Closed.restaurants.x3, Reopened.restaurants.x3,
                             Initially.reopened.restaurants.for.outdoor.dining.only,
                             rest.last.update))



###########################################################################
# Day Cares - days closed
df <- mutate(df, daycare.closed.days = ifelse(is.na(Reopened.child.care), 0,
                                              ifelse(is.na(Closed.day.cares), 0,
                                                    Reopened.child.care - Closed.day.cares)))

# Create indicator column for day cares
df <- mutate(df, daycare.flag = ifelse(daycare.closed.days > 0, 1, 0) )

# Drop unnecessary columns
df <- subset(df, select = -c(Closed.day.cares, Reopened.child.care))

###########################################################################
# Movies - days closed
df$movies.last.update <- seq(ISOdate(2021,3,4), ISOdate(2021,3,4), length.out = 51)

# Movies closed x1
# if close is there && reopen not there 
# then last date - close date
df <- mutate(df, movies.closed.days.x1 = ifelse(is.na(Closed.movie.theaters) == FALSE
                                                & is.na(Reopened.movie.theaters) == TRUE,
                                                movies.last.update - Closed.movie.theaters,
                                          # if close1 is there && reopen1 is there 
                                          # then reopen - close
                                          ifelse(is.na(Closed.movie.theaters) == FALSE
                                              & is.na(Reopened.movie.theaters) == FALSE,
                                              Reopened.movie.theaters - Closed.movie.theaters,
                                              0)))

# Movies closed x2
# if close2 is there && reopen2 is there 
# then reopen2 - close2
df <- mutate(df, movies.closed.days.x2 = ifelse(is.na(Closed.movie.theaters.x2) == FALSE
                                          & is.na(Reopened.movie.theaters.x2) == FALSE,
                                          Reopened.movie.theaters.x2 - Closed.movie.theaters.x2,
# if close2 is there && reopen2 is not there 
# then last update - close2
                                        ifelse(is.na(Closed.movie.theaters.x2) == FALSE
                                               & is.na(Reopened.movie.theaters.x2) ==  TRUE,
                                               movies.last.update - Closed.movie.theaters.x2,
                                               0)))

# if close is not there && close2 is NA && close3 is NA (South Dakota rule)
# then 0

# Movies - total duration closed
df <- mutate(df, movies.duration.days = movies.closed.days.x1 + movies.closed.days.x2)

# Create indicator column for day cares
df <- mutate(df, movies.flag = ifelse(movies.duration.days > 0, 1, 0) )


# delete unnecessary columns
df <- subset(df, select = -c(Closed.movie.theaters, Reopened.movie.theaters,
                                     Closed.movie.theaters.x2, Reopened.movie.theaters.x2,
                                     movies.last.update))


###########################################################################
# Gyms - days closed
# Reopened.gyms.x2 has 01/4/2021 as the last date
df$gym.last.update <- seq(ISOdate(2021,3,4), ISOdate(2021,3,4), length.out = 51)

# Gym closed x1
# if !closed & !closed2
# then 0
# if closed & reopened
# then reopened - closed
# if closed & !reopened
# then last update - closed
df <- mutate(df, gym.closed.days.x1 = ifelse(is.na(Closed.gyms) & is.na(Closed.gyms.x2), 0,
                                        ifelse(!is.na(Closed.gyms) & !is.na(Reopened.gyms),
                                               Reopened.gyms - Closed.gyms,
                                          ifelse(!is.na(Closed.gyms) & is.na(Reopened.gyms),
                                               gym.last.update - Closed.gyms, NA))))

# Gym closed x2
# if closed2 & reopened2
# then reopened2 - closed2
# if closed2 & !reopened2
# then last update - closed2
df <- mutate(df, gym.closed.days.x2 = ifelse(!is.na(Closed.gyms.x2) & !is.na(Reopened.gyms.x2),
                                              Reopened.gyms.x2 - Closed.gyms.x2,
                                        ifelse(!is.na(Closed.gyms.x2) & is.na(Reopened.gyms.x2),
                                              gym.last.update - Closed.gyms.x2,
                                              0)))

# Gym - total duration closed
df <- mutate(df, gyms.duration.days = gym.closed.days.x1 + gym.closed.days.x2)

# Create indicator column for day cares
df <- mutate(df, gyms.flag = ifelse(gyms.duration.days > 0, 1, 0) )


# Drop columns not needed for gyms
df <- subset(df, select = -c(Closed.gyms, Reopened.gyms,
                                     Closed.gyms.x2, Reopened.gyms.x2,
                                     gym.last.update))


# date set to 1899-12/31 when 0 in excel
# bars were closed a 3rd time, re-opening for 3rd time is not in data
# religous gatherings were not closed, but were reopened.


#getwd()
#?read_xlsx
```

## NY COVID Death Data

```{r}
st_to_state <- function(x){
  state.abb[which(state.name == x)]
}

NYT_Data <- read_csv("https://raw.githubusercontent.com/nytimes/covid-19-data/master/us-states.csv")
total_covid <- NYT_Data %>% 
  group_by(state) %>% 
  arrange(desc(date)) %>% 
  slice(1) %>% 
  filter(!state %in% c("District of Columbia", "Guam", "Northern Mariana Islands", "Puerto Rico", "Virgin Islands")) %>% 
  mutate(state = st_to_state(state))

write_csv(total_covid, "covid_cases_deaths.csv")

```
## State Legislation

```{r}

legis_control <- read.csv(file = 'Legis Control - Sheet1.csv') 
legis_control_clean <-  legis_control %>% 
  mutate(state = st_to_state(State))

legis_control_clean <- subset(legis_control_clean, select = -c(State))
names(legis_control_clean)[names(legis_control_clean) == "state"] <- "State.Abbreviation"

```

## 2020 Population

```{r}

population_2020 <- read.csv(file = '2020_population.csv') 

names(population_2020)[names(population_2020) == "state"] <- "State.Abbreviation"
names(population_2020)[names(population_2020) == "pop"] <- "most_recent_population"
```

```{r}
#join data sets
join_1 <- full_join(df, df_emr, by = "State.Abbreviation")
join_2 <- full_join(join_1, df_facemsk, by = "State.Abbreviation")
join_3 <- full_join(join_2, df_stayhm, by = "State.Abbreviation")

#rename columns to the same column name to join
names(data_state_characteristics)[names(data_state_characteristics) == "state.abbreviation"] <- "State.Abbreviation"
names(total_covid)[names(total_covid) == "state"] <- "State.Abbreviation"

join_4 <- full_join(join_3, data_state_characteristics, by = "State.Abbreviation")
join_5 <- full_join(join_4, legis_control_clean, by = "State.Abbreviation")

#remove district of columbia
join_5 <- join_5[join_5$State.Abbreviation != "DC", ] 

#last join and rename as data_clean
join_6 <- full_join(join_5, population_2020, by = "State.Abbreviation")
data_clean <- full_join(join_6, total_covid, by = "State.Abbreviation")

#create new column COVID infections per capita
data_clean$infections.per.capita <- data_clean$cases / data_clean$most_recent_population

write_csv(data_clean, "data_clean.csv")

```

### EDA

```{r}
#read final data set for EDA
data_final <- read.csv(file = 'data_clean.csv') 

#here we plot counts of the party affiliation, since we're only looking 
#at democrats v.s. rep, we can remove the 2 outlier states
pos_hist <- ggplot(data_final, aes(x=Legislature.Control))+
  geom_bar(color="darkblue", fill="lightblue") +
  labs(title = "Bar Chart of State Legislature Party", size =5,
              x = "State Legislature Party)", y = "Count"
       ) 
pos_hist

#drop MN and NE then, one hot encode the party affilation variable
data_final <- data_final[data_final$State.Abbreviation != "MN", ] 
data_final <- data_final[data_final$State.Abbreviation != "NE", ] 
data_final <- data_final[data_final$State.Abbreviation != "WY", ] 

data_final <-data_final %>% 
  mutate(value = 1)  %>% 
  spread(Legislature.Control, value,  fill = 0 ) 

#drop extra column and rename to boolean indicator
data_final <- subset(data_final, select = -c(Dem))
names(data_final)[names(data_final) == "Rep"] <- "is.rep"

```
## Correlations and Scatter Plots

```{r}
#distribution of our output variable 

plot1 <- ggplot(data =data_final, aes(x=infections.per.capita)) + 
  geom_histogram(bins= 10, col="lightblue") +
  labs(title = "Infections Per Capita Distribution", x = "Infections Per Capita", y = "Count")
plot1
```


```{r}
#temp df without state variable
#data_final_all_num <- subset(data_final, select = -c(State.Abbreviation))
data_final_all_num <- subset(data_final, select = -c(State.Abbreviation, state, State.Control, date))

#data_final_all_num <- data_final_all_num %>%
#  select(infections.per.capita, everything())

#cor(data_final_all_num[-1], data_final_all_num$infections.per.capita) 

corr_infections <- data_final_all_num %>% 
  correlate() %>% 
  focus(infections.per.capita)
corr_infections

```
Note: top 3 negative correlations; mental.health, rest.duration, stay home duration
top 3 positive correlations; is.rep, poverty.line, pop density per square mile

top 6 corr regardless of sign: is.rep, mental.health, rest.duration, poverty line,
stayhome, movies.duration, facemsk.duration.days	

```{r}

is_repp_corr <- data_final_all_num %>% 
  correlate() %>% 
  focus(is.rep)
is_repp_corr
```

Now we run correlations across is.rep against all other variables to check if
there is possible multicollinearity against other input variables. There doesn't
seem to be anything that is near -1 or 1, that shows potential signs of a 
pure linear relationship. Taking note of face.mask, rest.duration, and mental.health
as variables with ~0.5 collinearity.

```{r} 
#create new df of the top 6-7 inputs we want to graph out a corr matrix for
#these are ones we will potentially use to start our "big" model with 

data_high_corr <- data_final_all_num %>%
  select(infections.per.capita, is.rep, mental.health.professionals.per.100.000.population.in.2019,
        rest.duration.days, percent.living.under.the.federal.poverty.line..2018.,population.density.per.square.mile,          movies.duration.days,stayhm.duration.days	,facemsk.duration.days	)

infections_party <- data_high_corr %>%
  ggplot(aes(x = is.rep, y=infections.per.capita)) +
  geom_point() +
  geom_smooth(method="lm") +
   xlab('Republican Boolean') +
   ylab('Infections Per Capita') 

infections_mental <- data_high_corr %>%
  ggplot(aes(x = mental.health.professionals.per.100.000.population.in.2019, y=infections.per.capita)) +
  geom_point() +
  geom_smooth(method="lm") +
   xlab('Mental Health Professionals Per 100,000') +
   ylab('Infections Per Capita') 

infections_rest_duration <- data_high_corr %>%
  ggplot(aes(x = rest.duration.days, y=infections.per.capita)) +
  geom_point() +
  geom_smooth(method="lm") +
   xlab('Rest Duration Days') +
   ylab('Infections Per Capita') 

infections_poverty <- data_high_corr %>%
  ggplot(aes(x = percent.living.under.the.federal.poverty.line..2018., y=infections.per.capita)) +
  geom_point() +
  geom_smooth(method="lm") +
   xlab('Percent living Under the Poverty Line') +
   ylab('Infections Per Capita') 

infections_pop_density <- data_high_corr %>%
  ggplot(aes(x = population.density.per.square.mile, y=infections.per.capita)) +
  geom_point() +
  geom_smooth(method="lm") +
   xlab('Population Density Per Square Mile') +
   ylab('Infections Per Capita') 

infections_movie <- data_high_corr %>%
  ggplot(aes(x = movies.duration.days, y=infections.per.capita)) +
  geom_point() +
  geom_smooth(method="lm") +
   xlab('Movie Theatres Closed in Days') +
   ylab('Infections Per Capita') 

infections_stay_home <- data_high_corr %>%
  ggplot(aes(x = stayhm.duration.days, y=infections.per.capita)) +
  geom_point() +
  geom_smooth(method="lm") +
   xlab('Stay at Home Order in Days') +
   ylab('Infections Per Capita') 

infections_face_mask <- data_high_corr %>%
  ggplot(aes(x = facemsk.duration.days, y=infections.per.capita)) +
  geom_point() +
  geom_smooth(method="lm") +
   xlab('Facemask Duration Days') +
   ylab('Infections Per Capita') 

(infections_party + infections_mental)/
  (infections_rest_duration+infections_poverty)

(infections_pop_density+infections_movie)/
  (infections_stay_home+infections_face_mask)

```

## Linear Regression

```{r}

#limited model 
limited_model <- lm(infections.per.capita ~ is.rep, 
            data = data_high_corr)

summary(limited_model)
```
```{r}

#second model
second_model <- lm(infections.per.capita ~ is.rep + population.density.per.square.mile + percent.living.under.the.federal.poverty.line..2018. + facemsk.duration.days
            ,data = data_high_corr)

summary(second_model)
```


```{r}

#third model
third_model <- lm(infections.per.capita ~ is.rep + 
        mental.health.professionals.per.100.000.population.in.2019 +
        rest.duration.days+ percent.living.under.the.federal.poverty.line..2018.
        +population.density.per.square.mile
        +movies.duration.days
        +stayhm.duration.days
        +facemsk.duration.days
            ,data = data_high_corr)

summary(third_model)
```
```{r}

#fourth model
fourth_model <- lm(infections.per.capita ~ is.rep + population.density.per.square.mile + I(population.density.per.square.mile^2) + I(population.density.per.square.mile^3) + percent.living.under.the.federal.poverty.line..2018. + facemsk.duration.days, data = data_high_corr)

summary(fourth_model)
```

```{r}
#get robust ses
rse <- function(model) { 
  sqrt(diag(vcovHC(model)))
}

#stargazer 
stargazer(
  limited_model, second_model, third_model, fourth_model,
  se = list(rse(limited_model), rse(second_model), rse(third_model), rse(fourth_model)), 
  type = 'text')
```



# CLM Assumptions on second_model

```{r}
data_high_corr_pred_resids <- data_high_corr%>% 
  mutate(
    fouth_model_preds = predict(fourth_model), 
    fourth_model_resids = resid(fourth_model)
  ) 

```


1. I,I.D

2. Linear Conditional Expectation

```{r}
data_high_corr_pred_resids %>% 
  ggplot(aes(fouth_model_preds, fourth_model_resids)) +
  geom_point() +
  stat_smooth()
```


```{r, message==FALSE}
data_high_corr_pred_resids %>% 
  ggplot(aes(is.rep, fourth_model_resids)) +
  geom_point() +
  stat_smooth()
```

```{r}
data_high_corr_pred_resids %>% 
  ggplot(aes(population.density.per.square.mile, fourth_model_resids)) +
  geom_point() +
  stat_smooth()
```

```{r}
data_high_corr_pred_resids %>% 
  ggplot(aes(percent.living.under.the.federal.poverty.line..2018., fourth_model_resids)) +
  geom_point() +
  stat_smooth()
```

```{r}
data_high_corr_pred_resids %>% 
  ggplot(aes(facemsk.duration.days, fourth_model_resids)) +
  geom_point() +
  stat_smooth()
```



3. No Perfict Collinearity

```{r}
vif(fourth_model)
```

4. Homoskedastic Error

```{r}
plot(fourth_model, which=3)
```


5. Normally Distributed Errors

```{r}
se_histo <- data_high_corr_pred_resids %>% 
  ggplot(aes(x = fourth_model_resids)) + 
  geom_histogram()
  
se_qq <- data_high_corr_pred_resids %>% 
  ggplot(aes(sample = fourth_model_resids)) + 
  stat_qq() + stat_qq_line()

se_histo / se_qq
```
































